Parsing Postfix log files

### 2009-02-23 doc/logparser-other-parsers-review.tex
Fixes for overfull hboxes.

Sawmill has three different Postfix log file parsers, extracting three
different sets to data:

@@

    \item
        \urlLastChecked{http://www.thesawmill.co.uk/formats/postfix.html}{2008/11/23}
        \newline{} Fields extracted: from, to, server, UID, relay, status,
        number of recipients, origin hostname, origin \acronym{IP} address,
        and virus.  It also counts the number of and total size of all
        mails delivered.  The fields \texttt{server}, \texttt{uid},
        \texttt{relay}, and \texttt{virus} are not explained in the
        documentation: \texttt{server} is probably the hostname or
        \acronym{IP} address of the server the mail is delivered to;
        \texttt{relay} might be the delivery method: \acronym{SMTP}, local
        delivery, or \acronym{LMTP}; \texttt{uid} might be the uid of the
        user submitting mail locally.  Postfix does not do any form of
        virus checking (though it has many options for cooperating with an
        external virus scanner), so the \texttt{virus} field is a mystery.

    \item
        \urlLastChecked{http://www.thesawmill.co.uk/formats/postfix_ii.html}{2008/11/23}
        \newline{} Fields extracted: from, to, RBL list, client hostname,
        and client \acronym{IP} address.  It also counts the number and
        total size of all mails delivered.

    \item
        \urlLastChecked{http://www.thesawmill.co.uk/formats/beta_postfix.html}{2008/11/23}
        \newline{} Fields extracted: from, to, client hostname, client
        \acronym{IP} address, relay hostname, relay \acronym{IP} address,
        status, response code, RBL list, and message id.  It also counts
        the number and size of all mails delivered, processed, blocked,
        expired, and bounced.

@@

The Debian project (\urlLastChecked{http://www.debian.org/}{2008/11/23})
provides a manual page with the copy of anteater it distributes, so the
author was at least able to run anteater with the correct arguments; sadly
anteater produced zero for every statistic, presumably because it was
unsuccessful in parsing the log lines.

>>>>

Sawmill has three different Postfix log file parsers, extracting three
different sets of data:

@@

    \item \urlLastChecked[\hfill{}\newline{}]{http://www.thesawmill.co.uk/formats/postfix.html}{2008/11/23}.
        Fields extracted: from, to, server, UID, relay, status, number of
        recipients, origin hostname, origin \acronym{IP} address, and
        virus.  It also counts the number of and total size of all mails
        delivered.  The fields \texttt{server}, \texttt{uid},
        \texttt{relay}, and \texttt{virus} are not explained in the
        documentation: \texttt{server} is probably the hostname or
        \acronym{IP} address of the server the mail is delivered to;
        \texttt{relay} might be the delivery method: \acronym{SMTP}, local
        delivery, or \acronym{LMTP}; \texttt{uid} might be the uid of the
        user submitting mail locally.  Postfix does not do any form of
        virus checking (though it has many options for cooperating with an
        external virus scanner), so the \texttt{virus} field is a mystery.

    \item \urlLastChecked[\hfill{}\newline{}]{http://www.thesawmill.co.uk/formats/postfix_ii.html}{2008/11/23}.
        Fields extracted: from, to, RBL list, client hostname, and client
        \acronym{IP} address.  It also counts the number and total size of
        all mails delivered.

    \item \urlLastChecked[\hfill{}\newline{}]{http://www.thesawmill.co.uk/formats/beta_postfix.html}{2008/11/23}.
        Fields extracted: from, to, client hostname, client \acronym{IP}
        address, relay hostname, relay \acronym{IP} address, status,
        response code, RBL list, and message id.  It also counts the number
        and size of all mails delivered, processed, blocked, expired, and
        bounced.

@@

The Debian Linux distribution
(\urlLastChecked{http://www.debian.org/}{2008/11/23}) provides a manual
page with the copy of anteater it distributes, so the author was at least
able to run anteater with the correct arguments; sadly anteater produced
zero for every statistic, presumably because it was unsuccessful in parsing
the log lines.
